%-------------------------
% Resume in Latex
% Author : Dilip Teja
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{paralist} % for inline lists
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Dilip Teja} \\ \vspace{1pt}
    \vspace{1pt} \\ Flat No. Satyam-G2, Fortune Kum Kum Heights, Kondapur, Hyderabad-500084 India. \\ \vspace{2pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-7731026291 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{tejadilip23898@gmail.com}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/dilipteja}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/dilipteja1}}
    
\end{center}


%-----------EDUCATION-----------
\section{ACADEMIC QUALIFICATION}
  \resumeSubHeadingListStart
  
                \resumeSubheading
                    {National Institute of Technology, Warangal}{Warangal, India}
                    {Bachelor of Technology in Electronics and Communication - 7.4/10}
                    {Jun 2016 -- May 2020}

                \resumeSubheading
                   {Sri Chaitanya Institutions}{Hyderabad, India}
                   {Intermediate (+1 and +2) – 98.4/100}{May 2016}      

                \resumeSubheading
                   {Sri Chaitanya School}{Hyderabad, India}
                   {Class X – 9.7/10}{May 2014}       
   
  \resumeSubHeadingListEnd

%-----------RELEVANT COURSES-----------
\section{RELEVANT COURSES}
\begin{inparaitem}
\item Computer Programming
\item Data Structures and Algorithms 
\item Computer Networks
\item Computer Architecture and Organisation
\item Object-Oriented Programming 
\item Operating systems
\item Optimization Techniques
\item Engineering Mathematics
\item Digital System Design
\item Probability Theory
\item Digital Signal Processing
\item Microprocessors 
\end{inparaitem}


%-----------EXPERIENCE-----------
\section{WORK EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      		{Qualcomm India Private Limited}{Hyderabad, India }
      		{\textbf{Software Engineer}}{Dec 2021 -- Present}
      		\resumeItemListStart
        			\resumeItem{ Responsible for validating Linux Kernel and Linux 																					Security components for Qualcomm IoT chipsets 																						(Wearables, Connected Cameras, Industrial IoT products) 																	and part of five successful product releases.}
        			\resumeItem{Developed and integrated logging mechanism for stability 								 			 						test framework using Python, which provides MTBF 													    						reports.}
                    \resumeItem{Created more than 10 process improvement designs 											 									out of which four are in execution phase.}
        	\vspace{-15pt}
      		\resumeItemListEnd
            
      \resumeSubheading       
      		{}{}      
      		{\textit{\textbf{Associate Software Engineer}}}{Jun 2020 -- Nov 2021}
            \resumeItemListStart
        			\resumeItem{Built Kernel Automation Framework and automated more 					 			            						 than 200 test cases (Scheduler, Memory) using \textbf{Python,                                                     													OOPS, and Design Patterns}.}
        			\resumeItem{Developed Web Portal having more than 100 active users 								                using\textbf{ Django, Javascript, Ajax, Bootstrap, PostgreSQL}                                                   and deployed using Apache server.}
                    \resumeItem{The Web App provides data analytics and product information improving the team's productivity.}
      		\resumeItemListEnd            
   
  \resumeSubHeadingListEnd
  
  
  %-----------INTERNSHIPS-----------  
\section{INTERNSHIP EXPERIENCE}
  \resumeSubHeadingListStart

     \resumeSubheading
        	{Qualcomm India Private Limited}{Hyderabad, India}
      		{\textbf{Interim Engineering Intern}}{Apr 2019 -- Jun 2019}     
            \resumeItemListStart
                  \resumeItem{Developed end-to-end Automation for a nightly trigger of 												 test jobs, which improved the resource utilization by 30\%.}
                  \resumeItem{Developed a Web App as a one stop solution for the team to   				                          check and analyze test reports, improving efficiency.}         
                 \resumeItem{Implemented the App using \textbf{Python Flask, Ajax, Bootstrap,                                            PostgreSQL} and deployed using Apache server.}
           \resumeItemListEnd

    \resumeSubheading
      		{Indian Institute of Science, Bangalore (IISc)}{Bangalore, India}
      		{\textbf{Research Intern --- Guide}:Dr.Amarjot Singh,Founder \& CEO at SkyLark 														Labs Inc. }{Apr 2018 -- Jun 2018}       
      		\resumeItemListStart
        		 \resumeItem{Research on Transfer Learning and its applications.}         
        		 \resumeItem{Trained a ResNet model with augmented data for detecting and classifying gender and age.}
            \resumeItemListEnd             
 
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{RELEVANT PROJECTS}
    \resumeSubHeadingListStart
    
      	\resumeProjectHeading
          		{\textbf{Underage Kids Identification} $|$ \emph{Deep Learning, Keras}}{Aug 2018}
          		\resumeItemListStart
             			\resumeItem{Developed a Compact Stagewise \textbf{Regression Network}                                                    and Face Recognition using \textbf{Incremental Classifier}.}
            			\resumeItem{This model detects or recognizes underage kids                                                                  to prevent them from performing restricted activities.}
            			\resumeItem{Performed fine-tuning of a pre-trained model with                                                       augmented data and could achieve around 89\% accuracy.}            
          		\resumeItemListEnd
                
          \vspace{-15pt}
        \resumeProjectHeading
             	{\textbf{Online Voting System} $|$ \emph{Blockchain }}{Oct 2019}
          		\resumeItemListStart
              			\resumeItem{Developed Blockchain and implemented \textbf{Smart                                                                 Contracts} for voting in elections to prevent malpractices.}
            			\resumeItem{Accomplished as part of Microsoft CodeFunDo++ 															competition and secured \textbf{second place} across the                                                               college.}
          		\resumeItemListEnd
                
          \vspace{+5pt}      
         \resumeProjectHeading
           {\textbf{Line Follower} $|$ \emph{Arduino}} {Oct 2017}
          \resumeItemListStart
            		\resumeItem{Designed a line follower using Arduino UNO as part of 													the Hackathon.}
             		\resumeItem{The prototype follows a particular line detected 												               using an Arduino board and its attached sensors.}  
          \resumeItemListEnd 
          
       \vspace{-15pt}
      \resumeProjectHeading
          	{\textbf{A Novel OFDM scheme for Visible Light Communications } $|$ 								\emph{Matlab}}{Nov 2019}
          	\resumeItemListStart
            		\resumeItem{Implemented a spectral efficient OFDM scheme using 														the \textbf{Index Modulation} technique. }
             		\resumeItem{Monitored a spectral gain of 0.875 bits/s/Hz with OFDM-IM 											compared to conventional OFDM.}
                    \resumeItem{Spectral gain of OFDM-IM improved data transfer rates 												    compared to conventional VLC techniques.}
                    \resumeItem{Worked under the guidance of Prof V.V Mani, NIT 														Warangal}            		     
          \resumeItemListEnd 
   
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={\roman*}]
    \small{\item{
             \textbf{Languages:}{\hspace{3cm} Python, C, C++, Java(basics), Matlab(Basics)} 
             \\ \vspace{+1.5pt}
             {\textbf{Web Development:}}{ \hspace{1.570cm}Django, HTML/CSS, Javascript, 															Ajax, Jquery, PostgreSQL}
             \\ \vspace{+1.5pt}
             \textbf{Developer Tools:}{\hspace{2.090cm}VS Code, Jupyter Notebook, Pycharm, 													Google Colab } 
             \\ \vspace{+1.5pt}
             \textbf{Technologies/Frameworks:}{\hspace{0.470cm}Linux Kernel, Keras, Git, 																			GitHub} 		
             \\
    }}
 \end{itemize}


%-----------CO-CURRICULARS-----------
\section{ACHIEVEMENTS/CO-CURRICULAR/EXTRACURRICULAR}
\resumeItemListStart      
        	\resumeItem{Recipient of ”Orion Insta Award” from Senior Director at                                                 Qualcomm for outstanding contribution and efforts. 2021}
            \resumeItem{Three time recipient of ”Passionate Executor Award” at 													Qualcomm for driving execution within deadlines. 2021}
            \resumeItem{Achieved \textbf{All India Rank 602} in IIT-JEE  Mains among                                          over 1.2 million candidates. 2016}
            \resumeItem{Secured \textbf{State Rank 512} in TS-EAMCET organized under 											Ministry of HRD, \textbf{Govt. of Telangana}. 2016}
            \resumeItem{Secured \textbf{State Rank 1206} in AP-EAMCET organized under 										Ministry of HRD,\textbf{ Govt. of Andhra Pradesh}. 2016}
            \resumeItem{Professional Badminton Player, participated in state level 												tournaments. 2012 - Present}
  \resumeItemListEnd
  
  
  %-----------LEADERSHIP-----------
\section{LEADERSHIP ROLES}
 \resumeSubheading 
      {National Institute of Technology, Warangal}{Warangal, India}      
      {Inter-NIT Championships}{Jun 2018 - Jun 2020}
      \resumeItemListStart     
        	\resumeItem{Led college Badminton Team as a captain to quarter-finals.}
      \resumeItemListEnd  
      
 \vspace{-15pt}
 \resumeSubheading 
      {}{}      
      {Batch Representative}{Aug 2019 - Mar 2020}
      \resumeItemListStart      
        	\resumeItem{Represented the ECE Class of 2020 in the Department UG 												Council and other department events.}
        	\resumeItemListEnd
            
   \vspace{-15pt}
  \resumeSubheading 
      {}{}      
      {Sponsorship and Public Relations Sub-Coordinator}{Aug 2018 - Mar 2019}
      \resumeItemListStart      
            \resumeItem{Responsible for organizing the college's cultural festival 'Spring                                     Spree' and dealing with various sponsors, notably Harvard                                              Ascend and GameRoom.}
            \resumeItemListEnd
            
 \vspace{-15pt}
 \resumeSubheading 
      {}{}      
      {Electronics Club Team Member}{Aug 2017 - May 2018}
      \resumeItemListStart      
        	\resumeItem{Involved in conducting various events, notably the Arduino                                             Workshop and the Circuits Workshop.}
      \resumeItemListEnd
      
\end{document}
